Toward dynamic models of combat or lack thereof in animal mating

### 2016-01-18 ms.tex
small ms.tex changes

\citep{Gillespie-1976}

We generate the reaction events then step through them with a population.
\clearpage
\subsection{Naive Event Algorithm}
we have 3 lists
\begin{verbatim}
    immature males
    searching males
    nests
\end{verbatim}

@@

\subsection{Contest Algorithm}
See Fig. \ref{fig:contests}.
For a defender $x_{def}$ vs an attacker $x_{atk}$, there are 3 (currently 2) stages:
each individual has an aggression trait $a$ and a mass $m$.
\begin{equation}\label{eq:logit}
    logit^{-1}(\alpha) = \frac{exp(\alpha)}{1 + exp(\alpha)}
\end{equation}

@@

In the display phases the probability of escalation is dependent on the visible traits of x and x'

After the contest Energy costs are deducted from both the winner and the loser.
The winner also has a chance to abandon the RR (based off a trait).
If a death occurs (Energy(x) less than 0) then x is removed from the individual pool.

Traits:
\begin{enumerate}
    \item Visible to opponent:
    \begin{enumerate}
        \item Size, influenced by time entered maturity
    \end{enumerate}
    \item invisible to opponent:
    \begin{enumerate}
        \item Energy level, influenced by size and past actions
        \item Abandon Rate, influences RR abandonment rate
        \item Aggressiveness, influences escalation in contests
        \item Encounter Rate, influences chance of being selected for an event
    \end{enumerate}
\end{enumerate}
\clearpage

I am not sure if this is the best way to do this, the tables in plant are more aesthetic. 
\begin{table}[h!]
    \caption{Variable names and definitions in the model.}
    \centering
    \begin{tabular}{c | c | l }
        \hline
        Symbol & unit & Description\\
        \hline
        \hline
        $K$ & & number of individual males \\
        $N$ & & number of nests \\
        $R_i$ & & repoductive value of nest of nest $i$\\
        $\bar{R}$ & & average repoductive value of nest\\
        \hline
        $t_m$ & & the time at which the females begin to mature\\
        $S(t)$ = exp($-k_it$) & & The probability of an individual surviving to time t.\\
        \hline
        $m$ & $kg$ & mass\\
        $m_mat$ & $kg$ & The size at which 50\% of the population is mature.\\ 
        \hline
    \end{tabular}
\end{table}

>>>>

\citep{Gillespie-1976}
I think we would generate the reaction events then step through them with a population.

\clearpage
\subsection{Naive Event Algorithm}
we have 3 lists
\begin{verbatim}
    immature males
    searching males
    nests
\end{verbatim}

@@

\clearpage
\subsection{Contest Algorithm}
See Fig. \ref{fig:contests}.
For a defender $x_{def}$ vs an attacker $x_{atk}$, there are 3 (currently 2) stages:
each individual has an aggression trait $a$ and a mass $m$.
\begin{equation}\label{eq:logit}
    logit^{-1}(\alpha) = \frac{exp(\alpha)}{1 + exp(\alpha)}
\end{equation}

@@

After the contest Energy costs are deducted from both the winner and the loser.

The winner also has a chance to abandon the RR (based off a trait).\\

If a death occurs (Energy(x) less than 0) then x is removed from the individual pool.

Traits:
\begin{enumerate}
    \item Visible to opponent:
    \begin{enumerate}
        \item Size/Mass, influenced by time entered maturity
    \end{enumerate}
    \item invisible to opponent:
    \begin{enumerate}
        \item Abandon Rate, influences RR abandonment rate
        \item Aggressiveness, influences escalation in contests
        \item Encounter Rate, influences chance of being selected for an event
    \end{enumerate}
\end{enumerate}
\clearpage

I am not sure if this is the best way to do this, the tables in plant are more aesthetic. 
\begin{table}[h!]
    \caption{Variable names and definitions in the model.}
    \centering
    \begin{tabular}{c | c | l }
        \hline
        Symbol & unit & Description\\
        \hline
        \hline
        $K$ & & number of individual males \\
        $N$ & & number of nests \\
        $R_i$ & & repoductive value of nest of nest $i$\\
        $\bar{R}$ & & average repoductive value of nest\\
        \hline
        $t_m$ & & the time at which the females begin to mature\\
        $S(t)$ = exp($-k_it$) & & The probability of an individual surviving to time t.\\
        \hline
        $m$ & $g$ & mass\\
        $m_mat$ & $g$ & The size at which 50\% of the population is mature.\\
        $E$ & kJ & kiloJoules\\
        \hline
    \end{tabular}
\end{table}
